---
title: "GEO 880 - week 6 - Tasks and Inputs"
author: "Lars Weidinger"
date: "today"
format: 
  html:
    fig_caption: true
    fig-align: center
    highlight: tango
    number-sections: false
    code-fold: true
    theme: lumen
    embed-resources: true
    toc: true
    toc_depth: 2
    toc_float: true
execute:                      # Set global options for execution of code blocks
  echo: true                  # False = no code printed
  warning: false
  message: false
editor: visual
---

<!-- The following html code fragment produces fully justified text alignment -->

```{=html}
<style>
body {text-align: justify}
</style>
```

# Preliminaries

## Set Options

```{r}
options(warning = FALSE)    # Don't show warnings
```

## Install or Load packages

```{r}
#| code-fold: show
library(pacman)

# Load and if not found in the library will attempt to install the package
pacman::p_load(here,
               sf,
               readr,
               tmap,
               dplyr,
               ggplot2,
               tidyr,
               SimilarityMeasures,
               lubridate,
               plotly,
               terra, 
               tmap,
               install = TRUE)
```

## Store relevant CRS

```{r}
crs_lv03  <- 21781
crs_lv95  <- 2056
crs_wgs84 <- 4326
```

# Task 1: Import and visualize spatial data

## Boar
```{r}
wildschwein_BE <- read_delim("data/wildschwein_BE_2056.csv", ",") |>
    st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)
```

## Import
```{r}
fanel <- read_sf("data/Feldaufnahmen_Fanel.gpkg")
```

## What information does the dataset contain?
```{r}
head(fanel)

summary(fanel)
```

## What is the geometry type of the dataset (possible types are: Point, Lines and Polygons)?
Polygon

## What are the data types of the other columns?
FieldID = numeric, dbl  
Frucht = Character  

## What is the coordinate system of the dataset?
```{r}
st_crs(fanel)
```

# Task 2: Annotate Trajectories from vector data
```{r}
wildschwein_summer <- wildschwein_BE |>
  filter(
    (DatetimeUTC >= "2014-05-01" & DatetimeUTC < "2014-06-30") |
    (DatetimeUTC >= "2015-05-01" & DatetimeUTC < "2015-06-30")
  )
```

```{r}
# join the two datasets
wildschwein_summer <- st_join(wildschwein_summer, fanel)

# visualisation
ggplot(fanel) +
  geom_sf(aes(fill = Frucht)) +
  geom_sf(data = wildschwein_summer)
```

# Task 3: Explore annotated trajectories
```{r}

```

# Task 4: Import and visualize vegetationindex (raster data)
```{r}
vegetation_index <- terra::rast("data/vegetationshoehe_LFI.tif")

plot(vegetation_index)
```

# Task 5: Annotate Trajectories from raster data
```{r}
# x = spatial raster, y = spatial vector (points, lines, polygons, df or matrix)
vegetation_index_df <- terra::extract(x = vegetation_index, y =  wildschwein_BE)

wildschwein_BE <- cbind(wildschwein_BE, vegetation_index_df)

head(wildschwein_BE)
```
